\documentclass{cv}

\usepackage[left=0.75in,top=0.75in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{array,tabularx,ltablex}
\usepackage{scrextend}
\usepackage{etaremune,enumitem,calc}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Nicholas J. Derr} % Your name
\address{Massachusetts Institute of Technology}
\address{Cambridge, MA 02141}
\address{Mathematics Department}
\phone{920-382-2939}
\email{derr@mit.edu}
\wsite{https://www.njderr.com}

%\address{Pierce Hall, Room 413} % Your address


\usepackage{color,xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{iexec}

\newcommand\bluelink[2]{\href{#1}{\textcolor{blue}{#2}}}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{0em}
\newlength{\bibsep}
 {\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=[\arabic*],align=left,resume,leftmargin=*,%
        labelwidth=1.25em,
        labelsep=*,
        itemsep=\bibsep,parsep=0pt,partopsep=0pt,
        topsep=0pt}
%\let\oldendbibenum\endbibenum
%\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}

\newenvironment{bibenum*}
  {\renewcommand\labelenumi{\makebox[1.25em][l]{[\theenumi]}}%
   \etaremune[
     topsep=0pt,
     itemsep=\bibsep,
     labelwidth=1.25em,
     parsep=0pt,partopsep=0pt,leftmargin={\labelsep+\labelwidth}]}
  {\endetaremune}

\makeatother

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{cvSection}{Education}

  \school{
    Harvard University
  }{
    S.M.\@ 2019, Ph.D.\@ 2022
  }{
    Applied Mathematics
  }

  \school{
    Cambridge University
  }{
    M.A.St.\@ with Merit, 2016
  }{
    Applied Mathematics (Part III)
  }

  \school{
    University of Wisconsin--Madison
  }{
    B.S.\@ with Distinction, 2015
  }{
    Applied Math, Engineering \& Physics; Astronomy-Physics
  }

\end{cvSection}

\begin{cvSection}{Publications}
\begin{bibenum*}
  \item \iexec{../doi2cite.py -t tex 10.1073/pnas.2105338118 -e "N.J. Derr"}
  \item \iexec{../doi2cite.py -t tex 10.1103/PhysRevLett.125.158002 -e "N.J. Derr"}
  \item \iexec{../doi2cite.py -t tex 10.1029/2019GL083022 -e "N.J. Derr"}
  \item \iexec{../doi2cite.py -t tex 10.1029/2018JE005717 -e "N.J. Derr"}
\end{bibenum*}
\end{cvSection}

\begin{rSection}{Education}

{\bf Harvard University} \hfill S.M.\@ 2019, Ph.D.\@ 2022 
\\ Applied Mathematics
\\ Advisor: Prof.\@ Chris H.~Rycroft
	\\ Thesis: \textit{Modeling and simulation of fluid--structure interaction in physics and biology}\\
\\{\bf Cambridge University} \hfill M.A.St.\@ with Merit, 2016 
\\ Applied Mathematics
\\ Part III of the Mathematical Tripos
	\\ Essay: \textit{Artificial phoretic microswimmers} \\
\\{\bf University of Wisconsin--Madison} \hfill B.S.\@ with Distinction, 2015 
\\ Applied Math, Engineering and Physics (AMEP); Astronomy-Physics
\\ Certificates: Computer Science; Business
	\\ Thesis: \textit{An examination of trends in lunar exospheric potassium emission}
\end{rSection}


\begin{rSection}{Research Interests}
Continuum mechanics, poroelasticity, biomechanics, fluid-solid interaction, high-performance scientific computing, low-Reynolds number flow, cellular locomotion, numerical methods, elastoplasticity
\end{rSection}

\begin{rSection}{Experience}
%	\begin{tabularx}{0.9825\textwidth}{ @{} l  >{\raggedleft\arraybackslash}X}%@{\hspace{6ex}}l}
%		\textbf{NASA Goddard Space Flight Center}, Research Assistant & 2013-2016 \\
%		Advisor: Dr.~Ronald J.\@ Oliversen \\[0.5em]
%		\textbf{UW-Madison Physics Department}, Research Assistant & 2012-2014 \\
%		Advisor: Prof.~Edwin J.\@ Mierkiewicz
%	\end{tabularx}

%{\bf MIT Mathematics Department}, Instructor in Applied Mathematics \hfill {2022--} \\
Department of Mathematics, {\bf Massachusetts Institute of Technology} \hfill {2022--present}\\
	\mbox{}\hspace{2em}\textit{Instructor in Applied Math}\\
\\John A.\@ Paulson School of Engineering and Applied Sciences, {\bf Harvard University} \hfill {2016--2022}\\
	\mbox{}\hspace{2em}\textit{Research Fellow}\\
\\Goddard Space Flight Center, {\bf NASA} \hfill {2013--2016}\\
	\mbox{}\hspace{2em}\textit{Research Assistant}\\
\\Department of Physics, {\bf University of Wisconsin--Madison} \hfill {2012--2014}\\
	\mbox{}\hspace{2em}\textit{Research Assistant}
\end{rSection}

\begin{rSection}{Awards/Fellowships}
	\vspace{-1em}
	{\setlength{\extrarowheight}{0.55em}
	\begin{tabularx}{1.0125\textwidth}{@{\hspace{15pt}}  >{\bfseries}l >{\raggedleft\arraybackslash}X}%@{\hspace{6ex}}l}
		 QBio Graduate Student Fellowship \ & \hspace{-1cm}NSF-Simons MathBio Center at Harvard, 2019-2022 \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.9\textwidth}X}{\small Provides 50\% tuition and stipend support for each academic year.}\\
		Certificate of Distinction in Teaching \ & \hspace{-1cm}Bok Center for Teaching and Learning, 2018-2022 \\
		NDSEG Fellowship \ & \hspace{-1cm}Department of Defense, 2015 (applied 2016-2019) \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.9\textwidth}X}{\small Provides full tuition and stipend support for three years. Approximately 200 awarded annually.}\\
		Marcus L. Urann Fellowship & Honor Society of Phi Kappa Phi, 2015 \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.9\textwidth}X}{\small Provides \$15,000 towards one year of graduate study. Six awarded annually.}\\[2em]
		Theodore Herfurth Award & UW--Madison, 2015 \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.95\textwidth}X}{\small Awards  \$2,000 to the two (of 7,000) graduating students each year who have made the most effective use of their time at \mbox{UW--Madison}, demonstrating productivity in the classroom and commitment to the community.} \\
		AMEP Leadership Prize & UW--Madison Mathematics Department, 2015 \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.95\textwidth}X}{\small Given annually to an outstanding AMEP student with demonstrated leadership and solid academic record.} \\
		Hilldale  Undergraduate Research Fellowship & UW--Madison, 2014  \\[-0.25em]
		\multicolumn{2}{@{\hspace{25pt}}>{\hsize=0.9\textwidth}X}{\small Provides \$3,000 to support research with faculty sponsor. Approximately 100 awarded annually.}\\
		Academic Excellence Scholarship & WI Higher Education Aids Board, 2010 \\
		National Merit Scholarship  & 2010
	\end{tabularx}
	}
\end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Publications}

	\textbf{N.J.~Derr} and C.H.~Rycroft, \href{https://arxiv.org/abs/2206.14379}{\textcolor{blue}{\textit{A projection method for porous media flow}}}, arxiv: 2206.14379 (2022). In preparation.

	\textbf{N.J.~Derr}, T.~Dombrowski, C.H.~Rycroft, and D.~Klotsa, \href{https://arxiv.org/abs/2202.03669}{\textcolor{blue}{\textit{Reciprocal swimming at intermediate Reynolds number}}}, arxiv:2202.03669 (2022). Under revision.

	Y.L.~Lin, \textbf{N.J.~Derr}, and C.H.~Rycroft, \href{https://www.pnas.org/content/119/1/e2105338118}{\textcolor{blue}{\textit{Eulerian simulation of complex suspensions and biolocomotion in three dimensions}}}, Proceedings of the National Academy of Sciences \textbf{119}(1), e2105338118 (2022).

	\textbf{N.J.~Derr}$^*$, D.C.~Fronk$^*$, C.A.~Weber, A.~Mahadevan, C.H.~Rycroft, and L.~Mahadevan, \href{https://doi.org/10.1103/PhysRevLett.125.158002}{\textcolor{blue}{\textit{Flow-driven branching in a frangible porous medium}}}, Physical Review Letters \textbf{125}, 158002 (2020).

	S.A.~Rosborough, R.J.~Oliversen, E.J.~Mierkiewicz, M.~Sarantos, S.~Robertson, D.C.P~Kuruppuaratchi, \textbf{N.J.~Derr}, M.A.~Gallant, and F.L.~Roesler, \href{https://doi.org/10.1029/2019GL083022}{\textcolor{blue}{\textit{High-resolution potassium observations of the lunar exosphere}}}, Geophysical Review Letters \textbf{46}(12), 6964--6971 (2019). 

	D.C.P.~Kuruppuaratchi, E.J.~Mierkiewicz, R.J.~Oliversen, M.~Sarantos, \textbf{N.J.~Derr}, M.A.~Gallant, S.A.~Rosborough, C.W.~Freer, L.C.~Spalsbury, D.D.~Gardner, O.L.~Lupie, and F.L.~Roesler, \href{https://doi.org/10.1029/2018JE005717}{\textcolor{blue}{\textit{High-resolution, ground-based observations of the lunar sodium exosphere during the LADEE mission}}}, Journal of Geophysical Research: Planets \textbf{123}(9), 2430--2444 (2018).

	{\small * denotes equal contribution}
\end{rSection}

\begin{rSection}{Presentations}

	\textit{Fluid inertia and the scallop theorem}, SIAM Conference on the Life Sciences, Pittsburgh, July 11--14, 2022.

	\textit{A projection method for porous media simulation}, APS March Meeting, Chicago, March 14--18, 2022.

	\textit{A projection method for porous media simulation}, Computational and Applied Math Seminar at Tufts University, Medford, November 8, 2021.

	\textit{A projection method for porous media simulation}, SIAM Annual Meeting, Virtual, July 19--23, 2021.

	\textit{Swimming mechanisms at intermediate Reynolds number}, Third Annual Conference on Quantitative Approaches in Biology at Northwestern University, Evanston, November 19--21, 2020.

	\textit{Steady streaming in a simple reciprocal swimmer}, APS Division of Fluid Dynamics Annual Meeting, Seattle, November 23--26, 2019.

	\textit{Active phase separation in polymer gels}, Second Annual Conference on Quantitative Approaches in Biology at Northwestern University, Evanston, October 4--5, 2019.

	\textit{Active phase separation of biphasic polymer gels}, MathBio Journal Club at Brandeis University, Waltham, May 1, 2019.

	\textit{Active phase separation of biphasic polymer gels}, APS March Meeting, Boston, March 4--8, 2019.
%	\textit{Channeling and branching in frangible porous media}, APS March Meeting, Boston, March 4-8, 2019.

	\textit{Eulerian numerical methods for flow through poroelastic media}, APS Division of Fluid Dynamics Annual Meeting, Atlanta, November 18--20, 2018.

	\textit{Numerical simulations of isotropic active gels}, 16th Annual Northeastern Granular Materials Workshop, New Haven, June 8, 2018.

	\textit{Numerical simulations of activity-driven mechanical instabilities in gels}, APS March Meeting, Los Angeles, March 5--9, 2018.

	\textit{Fabry-Perot observations of lunar exospheric potassium emission}, UW--Madison Undergraduate Research Symposium, Madison, April 16, 2015.

	\textit{Fabry-Perot observations of lunar exospheric potassium emission}, NASA Goddard Space Flight Center Summer Intern Poster Session, Greenbelt, July 31, 2014.
\end{rSection}
\begin{rSection}{Current Research}
	With Prof.\@ L.\@ Mahadevan, Dr.\@ Christoph Weber, Prof.\@ Chris Rycroft:\\
	\begin{addmargin}{1em}
		\vspace{-1.7em}
		Phase separation, pattern formation, and structure emergence in cross-linked polymer gels subject to active stresses induced by fuel-dependent molecular motor binding dynamics%\\[0.3em]
%	Channel formation and branching dynamics in frangible porous media, mediated by a simple mechanical model relating erosion to local pressure gradients (with Dr.\@ David Fronk)
	\end{addmargin}

	With Prof.\@ Dave Mooney, Dr.\@ Kyle Vining, Prof.\@ Chris Rycroft:\\
	\begin{addmargin}{1em}
		\vspace{-1.7em}
		Modeling decreased collagen fiber formation within artificial extracellular matrices as a function of cross-linker mediated changes in rheology
	\end{addmargin}
\end{rSection}

\begin{rSection}{Programming}
	C\texttt{++} (OpenMP, MPI), Python (numpy, scipy, matplotlib), Mathematica, PETSc, Matlab, Java
\end{rSection}

\begin{rSection}{Teaching}
	\begin{tabularx}{0.9825\textwidth}{ @{} l @{\hspace{0.55in}}l >{\raggedleft\arraybackslash}X}%@{\hspace{6ex}}l}
		\textbf{Course} & \textbf{Instructor} & \textbf{Term} \\
		Applied Math 104: Complex and Fourier Analysis$^*$ & Prof.~Ariel Amir & Fall 2021\\
		Applied Math 205: Advanced Scientific Computing I$^*$ & Prof.~Chris Rycroft & Fall 2020\\
		Engineering Sciences 240: Solid Mechanics$^*$ & Prof.~Joost Vlassak & Fall 2019\\
		Applied Math 225: Advanced Scientific Computing II$^*$ & Prof.~Chris Rycroft & Spring 2019\\
		Engineering Sciences 220: Fluid Dynamics & Prof.~James Rice & Fall 2018 \\
		Applied Math 225: Advanced Scientific Computing II$^*$ & Prof.~Chris Rycroft & Spring 2018 \\[0.25em]
		\multicolumn{3}{@{\hspace{1em}}>{\hsize=0.95\textwidth}X}{\small$*$ Bok Certificate of Distinction in Teaching}\\ %\hspace{1em} %$\dagger$ Not eligible for Bok Certificate (low enrollment)}\\
	\end{tabularx}
\end{rSection}
\end{document}
